$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-15 paper/Referee-response.tex

\documentclass[12pt]{article}
\usepackage{fullpage}
\begin{document}
\noindent Dear editor,
\\

\noindent Thanks for sending us the referee responses. We would like to thank
the referee for their helpful comments and questions regarding our
paper. In response we have made changes to our manuscript and feel
these have improved the paper, we therefore hope our paper will now be
accepted for publication in PRD.
\\
\noindent We respond to each point raised by the referee below, explaining
where appropriate what we have done to address it in the paper.

\begin{itemize}
\item {\it ``in eq. (9) an additional parameter $\mu'$ appears.  Where
does it come from?  Even though it is later fixed to 5 TeV, it is not
clear if it has any impact on their study?  Even if it has no impact,
this should be stated somewhere.''}

The referee is correct to point out that the bilinear coupling $\mu'$ is
absent from the list of superpotential terms, and is lacking an explanation
in our original submission. The $\mu'$ term violates the $E_6$ symmetry, as
it is associated with the incomplete $27$ and $\overline{27}$ to which the
fields $\hat{H'}$ and $\hat{\overline{H}'}$ belong, but is invariant under
the Standard Model gauge group and the low energy $U(1)'$ symmetry. For this
reason it is not given in the superpotential in Eq.~(5). Additionally, because
this parameter does not appear in the EWSB conditions the impact from it on
the fine tuning can be neglected, and so fixing the value of $\mu'$ does not
impact the results.

To address this, we have added a short discussion immediately
following Eq.~(9) that explains the appearance of the additional parameter
and states that the chosen value of $\mu'$ does not impact on the fine
tuning in the study.

@@

This is an important point which we neglected to comment on in our
original article.  In the models we investigate numerically in our
paper, if gauge kinetic mixing is absent at the GUT scale it, the
radiatively induced gauge kinetic mixing will be rather small at the
EW scale as has been shown in the literature.  Therefore we neglected
this.  However the referee is correct that it is not the case in all
$U(1)$ extensions and this may have a significant impact on the
$Z^\prime$ mass limit.

To address this issue we have added remarks to the end of section III
explaining why it is small in the models we consider, with reference
to the previous literature and comment on how it will impact on tuning
results if one considers a case with large gauge kinetic mixing.

\item {\it ``page 13: the author state that the include leading
two-loop contributions to the Higgs mass.  Which are those?  Are the
corresponding contributions to the minimization equations 16 included
and, thus, in their measure of fine-tuning?  Concerning the two-loop part:
in eq. (9) the couplings $\kappa_i S D_i D_i$ are included.  As the extra
D-quarks have to be heavy, one would naively expect that they give a
sizable contribution to the Higgs masses at the 2-loop level, in particular
as they take in their numerical studies $|\lambda| \leq 3$.  Are those
included as well?''}

The referee is correct that we missed the references specifying what
we mean by the leading two-loop corrections, so this was unclear.  We
included leading two-loop corrections calculated using effective field
theory methods, which have been generalized from well known
calculations in the MSSM and NMSSM.

@@

To address this issue we have added references pointing out where we
obtained the leading two-loop Higgs corrections from.  For
completeness we also added a footnote pointing readers to the new tool
in the SARAH package which calculates the two-loop corrections to
Higgs masses in non-SUSY models.

We also understand why the referee may expect $\kappa$ couplings to give
a large contribution to the light Higgs mass, however we find that already
at one-loop the contribution from this coupling is small. The main reason
for this is the fact that singlet mixing with lightest Higgs is highly
suppressed in these models, which is a result of the large singlet VEV
required to meet the $Z^\prime$ limit.  The impact of the $\kappa$
couplings on the Higgs mass was also looked at in section 5.2.2 of
hep-ph/0510419.

The leading two-loop corrections to the effective potential are not
included in our calculation of the fine tuning.  Although the one-loop
effective potential corrections are important they are already smaller
than the RGE corrections and so we do not expect the two-loop
effective potential corrections to contribute at the same level as
the terms we include nor one which would significantly alter our
conclusions.

To address this we have added a comment specifying the precise one
loop corrections we use to the end of the paragraph below Eq.~(30).

### 2015-05-15 paper/e6ssm-tuning-paper.tex
Added comment on LEP bounds and CCB constraints

In this case we now consider realistic scenarios, where the
parameters that are not scanned over are set to values which keep the
associated states comfortably above their experimental limits.  So in
both the MSSM and E$_6$SSM, all other soft scalar masses are set
to $5$ TeV.  Since we work in the third family approximation, taking
the first and second generation Yukawa couplings to be zero, we also
assume their associated soft trilinears vanish.  Similarly we take
$A_b = A_\tau = 0$ GeV.  The $U(1)$ gaugino soft mass $M_1$ was fixed to
$M_1 = 300$ GeV, and we fix $M_3 = 2000$ GeV.  Additionally, in the
E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is held fixed with
$M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.

>>>>

In this case we now consider realistic scenarios, where the
parameters that are not scanned over are set to values which keep the
associated states comfortably above their experimental limits.  So in
both the MSSM and E$_6$SSM, all other soft scalar masses are set
to $5$ TeV.  In order to avoid being in conflict with LEP
bounds on the chargino mass \cite{Kraan:2005vy} we exclude those points for
which the lightest chargino mass $m_{\tilde{\chi}^\pm_1} < 104$ GeV\footnote{In
fact this requirement has no impact on the bounds we find for the fine tuning
below. We found that, in the parameter space covered by our scans, including
points that violate the LEP bound does not lower the minimum fine tuning that
is obtained}.  We also impose several theoretical constraints on the points
included in the analysis.  In particular, we require a valid spectrum with no
tachyonic states to exclude points which would have an unrealistic minimum,
for example due to the appearance of charge or colour breaking (CCB) minima.
As a further requirement in the MSSM we exclude any points that do not satisfy
the well known CCB constraint \cite{Casas:1995pd},
\begin{equation} \label{eq:MSSMCCBconstraint}
A_t^2 < 3 \left ( \mu^2 + m_{H_u}^2 + m_{Q_3}^2 + m_{u_3}^2 \right ),
\end{equation}
or the unbounded from below (UFB) constraint,
\begin{equation} \label{eq:MSSMUFBconstraint}
m_{H_d}^2 + m_{H_u}^2 + 2 \mu^2 > 2 B \mu .
\end{equation}
We work in the third family approximation, taking the first and second
generation Yukawa couplings to be zero, and we also assume their associated
soft trilinears vanish.  Similarly we take $A_b = A_\tau = 0$ GeV.  The $U(1)$
gaugino soft mass $M_1$ was fixed to $M_1 = 300$ GeV, and we fix $M_3 = 2000$
GeV.  Additionally, in the E$_6$SSM the $U(1)_N$ gaugino soft mass $M_1'$ is
held fixed with $M_1' = M_1 = 300$ GeV, and $\mu^\prime = 5$ TeV.
